---
title: "Melbourne Pedestrian Sensor Data"
author: "Earo Wang"
institution: "Dept. of EBS, Monash University"
date: "Jan 30, 2017"
output:
  xaringan::moon_reader:
    css: ["default", "myremark.css"]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

class: inverse, middle, center

## It's likely that everyone in the room </br> is part of the data.

---

layout: false

```{r setup, include = FALSE, echo = FALSE}
options(htmltools.dir.version = FALSE)
opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
			   fig.path = 'figure/', cache.path = 'cache/', 
			   fig.align = 'center', dev = 'png', fig.width = 8, fig.height = 6, 
			   fig.show = 'hold', cache = FALSE, external = TRUE,
         dev = 'CairoPNG')
read_chunk('ss2017.R')
```

```{r load}
```

.left-column[
  ## Pedestrian Sensors
]

.right-column[

The City of Melbourne has set up sensors counting pedestrians across the city
at hourly intervals since 2009. There have been 43 sensors installed till November,
2016.

```{r leaflet}
```
]

---

.left-column[
  ## Pedestrian Sensors
  ## Pedestrian Counts
]

.right-column[
* The data structure

```{r ped-print}
```
]

---

class: inverse, middle, center

## Quick warmup with two little examples

---

## Snapshot with line plots

```{r line, fig.width = 10, fig.height = 8}
```

---

## Small multiples by weekdays

```{r facet, fig.width = 10, fig.height = 8}
```

---

class: inverse, middle, center

## Your turn

---

.left-column[
  ## Download
]

.right-column[
* Open data Melbounre

    + [Pedestrian counts](https://data.melbourne.vic.gov.au/Transport-Movement/Pedestrian-volume-updated-monthly-/b2ak-trbp)

    + [Pedestrian sensor locations](https://data.melbourne.vic.gov.au/Transport-Movement/Pedestrian-sensor-locations/ygaw-6rzq)
]

---

.left-column[
  ## Download
  ## Warning!
]

.right-column[
* Not that big but *bigish* spatio-temporal data

* Chunks of missingness in serveral sensors

* Unexpected behaviours dominates the patterns in some sensors
]

---

class: inverse, middle, center

## Happy hacking data!

Slides on <http://bit.ly/ss2017-ped>
