---
title: "Melbourne Pedestrian Sensor Data"
author: "Earo Wang"
institution: "Dept. of EBS, Monash University"
date: "Jan 30, 2017"
output:
  xaringan::moon_reader:
    css: ["default", "myremark.css"]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

class: inverse, middle, center

## It's likely that everyone in the room </br> is part of the data.

???

What makes this data set interesting or appealing is that everybody in this
room contributes at least a little to the data.

---

layout: false

```{r setup, include = FALSE, echo = FALSE}
options(htmltools.dir.version = FALSE)
opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
			   fig.path = 'figure/', cache.path = 'cache/', 
			   fig.align = 'center', dev = 'png', fig.width = 8, fig.height = 6, 
			   fig.show = 'hold', cache = FALSE, external = TRUE,
         dev = 'CairoPNG')
read_chunk('ss2017.R')
```

```{r load}
```

.left-column[
  ## Pedestrian
  ### - Sensors
]

.right-column[

The City of Melbourne has set up sensors counting pedestrians across the city
at hourly intervals since 2009. There have been 43 sensors installed till November,
2016.

```{r leaflet}
```
]

???

How do you get recorded? Until most recent, there have been 43 sensors installed
to count pedestrians walking by across the downtown every hour since 2009.

This map shows the sensor locations. We can see Southern Cross Station and 
Burke Street Mall, etc. We would expect to see different pedestrian patterns
in the train stations and in the shopping mall.

---

.left-column[
  ## Pedestrian
  ### - Sensors
  ### - Counts
]

.right-column[
* The data structure

```{r ped-print}
```
]

???

This is how the data looks like. I only take a slice of the data, Feb 2016 here.

Date time attributes, Sensor IDs and their names. Most importantly, pedestrian
counts at every hour.

---

class: inverse, middle, center

## Quick warmup with two little examples

???

I'm giving you two basic plots of this data to let you take off later.

---

## Snapshot with line plots

```{r line, fig.width = 10, fig.height = 8}
```

???

For temporal data or time series data, we usually get straight to line plots.

---

## Small multiples by weekdays

```{r facet, fig.width = 10, fig.height = 8}
```

???

We can slice these lines into multiple pieces.

---

class: inverse, middle, center

## Your turn

---

.left-column[
  ## Download
]

.right-column[
* Open data Melbourne

    + [Pedestrian counts](https://data.melbourne.vic.gov.au/Transport-Movement/Pedestrian-volume-updated-monthly-/b2ak-trbp)

    + [Pedestrian sensor locations](https://data.melbourne.vic.gov.au/Transport-Movement/Pedestrian-sensor-locations/ygaw-6rzq)
]

???

Where's to download the data? Pedestrian data is the one of data projects host
on Open data Melbourne.

---

.left-column[
  ## Download
  ## Warning!
]

.right-column[
* Not that big but **bigish** spatio-temporal data

* Chunks of missingness in serveral sensors

* Unexpected behaviours dominate the patterns in some sensors
]

???

Friendly reminder.

Instead of working on the whole data set, Would suggest to work on the data after 
2013.

---

class: inverse, middle, center

## Happy hacking data!

Slides on <http://bit.ly/ss2017-ped>
